Visualisation of Brain Statistics with R-package `ggseg`

### 2019-04-12 draft_1_DVP.Rmd
Update draft_1_DVP.Rmd

`ggseg` is the main function for plotting 2D data.  
By default, the function automatically plots the DKT atlas (see Figure \@ref(fig:init)). 
`ggseg` function is a wrapper for `geom_polygon` from `ggplot2` and it can be built upon and combined like any ggplot object. 
The image plot consists of a simple brain representation containing no extra information. 
Hence, `ggseg` plots can be easily complemented with any of the available ggplot features and options.

@@

Representing brains as 2D polygons is a good solution for fast, efficient and flexible plotting, based on ggplot (a powerful tool for visualization) and that can be easily combined with interactive apps such as in shiny.
Yet brains are intrinsically 3D and it can be challenging to recognize the location of a region. This problem exacerbated in atlases representing subcortical structures – after all, cortical surfaces are 2D – such as grey matter structures or white matter tracts. 
Hence, here we also provide the ggseg3D function to plot, view and print 3D atlases in R. 
ggseg3D is based on tri-surface mesh plots using plotly. 
The data structure is somewhat more complex than the 2D ggplot polygon version and includes additional options for brain inflation, glass brains, camera locations, etc.  
As ggseg3D is based on plotly, the resulting brain atlases are interactive, which guides interpretation, and is useful for public dissemination. 
We recommend users to get a little familiarized with with [plotly](https://plotly-book.cpsievert.me/).

>>>>

`ggseg` is the main function for plotting 2D data.  
By default, the function automatically plots the DKT atlas (see Figure \@ref(fig:init)). 
`ggseg` function is a wrapper for `geom_polygon` from `ggplot2` and it can be built upon and combined like any ggplot object. 
The image plot consists of a simple brain representation containing no extra information. 
Hence, `ggseg` plots can be easily complemented with any of the available ggplot features and options. We recommend users to get familiarized with [ggplot2](https://ggplot2.tidyverse.org/) grammar.

@@

Representing brains as 2D polygons is a good solution for fast, efficient and flexible plotting, based on ggplot (a powerful tool for visualization) and that can be easily combined with interactive apps such as in shiny.
Yet brains are intrinsically 3D and it can be challenging to recognize the location of a region. This problem exacerbates in atlases that represent subcortical features – after all, cortical surfaces are 2D – such as grey matter structures or white matter tracts. 
Hence, here we also provide the ggseg3D function to plot, view and print 3D atlases in R. 
ggseg3D is based on tri-surface mesh plots using plotly. 
The data structure is somewhat more complex than the 2D ggplot polygon version and includes additional options for brain inflation, glass brains, camera locations, etc.  
As ggseg3D is based on plotly, the resulting brain atlases are interactive, which guides interpretation, and is useful for public dissemination. 
We recommend users to familiarize with [plotly](https://plotly-book.cpsievert.me/).
